---
title: "fireSense_FrequencyPredict"
author: "Jean Marchal"
date: "August 2016"
output:
  html_document: default
  pdf_document: default
---

# Overview
Predict fire frequencies from a model fitted using the fireSense_FrequencyFit module. These can be used to feed the ignition component of a landscape fire model (e.g fireSense).

# Download the module
```{r download module, eval = FALSE, echo = TRUE}
library(SpaDES)

moduleName <- "fireSense_FrequencyPredict"

workingDirectory <- tempdir() # Change this to a place you would like to put the model, if desired

downloadModule(moduleName, path = workingDirectory)
```

# Usage
```{r module_usage, eval = FALSE}
library(SpaDES)
library(magrittr)
library(raster)

set.seed(1)

## Make data
df <- data.frame(
  weather2 = rnorm(1000, 150, 30),
  fireFrequency = rpois(1000, .5)
)

## Make a typical output of fireSense_FrequencyFit
fireSense_FrequencyFitted <- list(
  formula = formula(fireFrequency ~ weather),
  family = poisson(),
  coef = setNames(0.01, "weather")
)
class(fireSense_FrequencyFit) <- "fireSense_FrequencyFit"

#outputDir <- file.path(tempdir(), "outputs")
times <- list(start = 1, end = 1)
parameters <- list(
  fireSense_FrequencyFit = list(
    f = 10, # Rescale predicted rates of fire count at any given temporal and spatial resolutions by a factor f = new_res / old_res
    mapping = list(weather2 = "weather"), # One can use the mapping arg to map variable's names in the data to those in the formula of the fitted object.
                                          # Here weather (formula) is mapped to weather2 (data).
    data = "df"
  )
)

modules <- list("fireSense_FrequencyPredict")
objects <- c("df", "fireSense_FrequencyFitted") # Pass objects found in the global environment to the simList environment.
paths <- list(
  # cachePath = file.path(outputDir, "cache"),
  modulePath = file.path("~/Documents/GitHub/McIntire-lab/modulesPrivate/") ## TODO: change this to tempdir()
  # inputPath = inputDir,
  # outputPath = outputDir
)
 
mySim <- simInit(times = times, params = parameters, modules = modules, objects = objects, paths = paths)

## TODO: raster layer/stack

spades(mySim)
```

# Events
Events are scheduled as follows:

- Module initiation
- Make predictions

## Saving
TODO: Write what is saved. (there is currently nothing saved, but this may change in the future)

# Data dependencies

## Input data
- An or several objects of class data.frame in which to look for variables with which to predict.
- An object of class fireSense_FrequencyFit, i.e. created with the fireSense_FrequencyFit module.

## Output data
An object whose class depends on those in input:

Input object class | Output object class
:-:|:-:
data.frame | vector
raster | raster
||

# Links to other modules
Predictions made using this module can be used to feed the ignition component of a landscape fire model (e.g fireSense).

